The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-06-12 docs/language_constraint_conll_camera_ready.tex
CoNLL camera ready 2.0 (Roy)
ack
ack

\section{Acknowledgments}
The authors thank several anonymous reviewers for helpful feedback. %\nascomment{anyone else?  who read drafts?} 
This research was supported in part by DARPA under the Communicating with Computers program.

>>>>

\section{Acknowledgments}
The authors thank Chenhao Tan and several anonymous reviewers for helpful feedback. %\nascomment{anyone else?  who read drafts?} 
This research was supported in part by Darpa CwC program through ARO (W911NF-15-1-0543), Samsung GRO, NSF IIS-1524371, and gifts from Google and Facebook.
